Create Figures and Tables

### 2023-08-30 Writing/NatureWater/2ndRoundRevision/replies/reply_to_reviewers_R2.tex

\author{}
\date{\vspace{-2.5em}}

\begin{document}

\section{Changes unrelated to reviewers' comments}

\textcolor{blue}{We made a small correction to our codes. In the previous round, we included counties with only irrigated acres for the irrigation share regression. For such counties, the share of irrigated acres was calculated to be 1. Therefore, we dropped them. While it resulted in some minor changes in our results from those provided in the previous round, all the qualitative results and conclusions are the same as the previous rounds.}

@@

\section{Reply to reviewer \#1}

I have read the revised manuscript and the authors’ responses to my initial review. I think they have done a nice job in responding to the points I raised. Thus, I recommend acceptance after the authors address the minor points that I noted while reading the revised manuscript. Those points are as follows:

\textcolor{blue}{Thank you for your feedback on our manuscript. We have addressed all your comments and suggestions, and our replies to your comments can be found in blue below (original comments in black). Please take a look at our comments about a small change in our codes at the top as well.}

@@

\item Equations 1 and 2 – shouldn’t ``k'' be ``k=1'' – if not, please explain how k is determined. Also, explain ``K'' and how it was determined.

\textcolor{blue}{Please see line 327 for the explanation of what K represents and how K is selected. We added similar explanations for equation 2 at line 341.}

\item Lines 385-387 – Figure A.3 is not presenting results by aquifer thickness category. It is presenting results for three aquifer thicknesses, not categories. Please rewrite.

\textcolor{blue}{Figure A.3 indeed presents what we intended to present. Please note that we made similar changes for average productivity analysis in the main text as shown in Figures 4 and 5. While the irrigated yield regression (equation 1) uses aquifer thickness category, the irrigated share regression uses aquifer thickness as it is as a continuous variable. In our average productivity analysis, we use four aquifer thickness values: 10, 40, 70, and 100 meter. For example, for the analysis of 10 meter, estimated yield response function for the first category is used as it falls within the [9m, 30.1 m] range. Estimated irrigation share for 10 meter can be obtained simply by plugging 10 into the trained model of the share of irrigated acres. In our initial submission, we were doing the same kind of analysis (using one number from each aquifer thickness category), but reported by category. In the previous round of revision, we decided to have two aquifer thickness values in the 3rd quantile category (90 and 130 meter). This is in response to another reviewer's point that it is not clear if indeed the impact of aquifer thickness on average productivity is non-linear as we claimed in our initial submission. Given the chosen series of aquifer thickness numbers are equi-distance, it has become much easier to observe the non-linearity in the impact of saturated thickness on overall productivity. Please note that we now present results for 10, 40, 70, and 100 meters, which are in the first, second, third, and third saturated thickness categories. }

@@

\item Figure B.1 – y-axis label is not correct – this should be ``Decline in Estimated….''.

\textcolor{blue}{Thank you for catching this. Fixed.}

\item Lines 398-407 – this paragraph needs to be rewritten. Use of ``demeaning'' or ``demeaned'' is incorrect. My guess is that the authors mean something like ``detrending'' or ``detrended'' – please revise. Also, fix noun-verb disagreement, etc. in this paragraph.

\textcolor{blue}{We understand that demeaning sounds wrong, however, it is a term that is used specifically for the types of operations we are conducting in that analysis in Economics.}

### 2023-08-30 Codes/1_Analysis.rmd
updates on the manuscript

main_analysis <-
  reg_data %>%
  rowwise() %>%
  dplyr::mutate(sc_base = "31011") %>%
  #--- the same sequence used for all the bootstrap iterations ---#
  dplyr::mutate(balance_seq = list(
    seq(
      min(data$balance),
      max(data$balance),
      length = 100
    )
  )) %>%
  dplyr::mutate(sat_seq_eval = list(
    c(10, 50, 90, 130)
  )) %>%
  dplyr::mutate(share_reg_data = list(
    data %>%
      .[, comp := sum(ir == "nir" | ir == "ir"), by = .(sc_code, year)] %>%
      .[comp == 2, ] %>%
      .[, acres_ratio := acres / sum(acres), by = .(sc_code, year)] %>%
      .[ir == "ir" & ir_area_ratio >= 0.75, ] %>%
      .[, balance_avg := mean(balance), by = sc_code]
  )) %>%
  #--- the same sequence used for all the bootstrap iterations ---#
  dplyr::mutate(sat_seq = list(
    share_reg_data[, seq(min(sat),
      max(sat),
      length = 100
    )] %>%
      c(., sat_seq_eval)
  )) %>%
  #--- values of the controls to be used in prediction ---#
  dplyr::mutate(
    sandtotal_med = median(share_reg_data$sandtotal_r),
    silttotal_med = median(share_reg_data$silttotal_r),
    awc_med = median(share_reg_data$awc_r)
  ) %>%
  #++++++++++++++++++++++++++++++++++++
  #+ Main analysis
  #++++++++++++++++++++++++++++++++++++
  dplyr::mutate(yield_analysis_results = list(
    yield_analysis(data, balance_seq, sat_seq_eval, sat_breaks, sat_text_data, sc_base)
  )) %>%
  dplyr::mutate(
    yield_pred_data = list(yield_analysis_results$yield_pred_data),
    yield_semi_res = list(yield_analysis_results$semi_res)
  ) %>%
  dplyr::mutate(yield_dif_test = list(
    lapply(
      2:3,
      \(x) {
        test_dif_in_yield(
          balance_ls = seq(min(data$balance), max(data$balance), length = 50),
          base_q = 1,
          comp_q = x,
          yield_semi_res,
          sat_text_data,
          sc_base
        ) %>%
          .[, comp_q := x]
      }
    ) %>%
      rbindlist()
  )) %>%
  dplyr::mutate(share_pred_data = list(
    share_analysis(
      share_reg_data, 
      sat_seq, 
      sandtotal_med, 
      silttotal_med, 
      awc_med, 
      crop
    )
  )) %>%
  dplyr::mutate(avg_yield_pred_data = list(
    get_average_yield(yield_pred_data, share_pred_data)
  ))

@@

all_results <-
  main_analysis %>%
  #--- bootsrap data ---#
  dplyr::mutate(boot_results = list(
    parallel::mclapply(
      1:200,
      \(x) {
        print(x)

@@

        return(list(share_pred_data = share_pred_data, avg_yield_pred_data = avg_yield_pred_data))
      },
      mc.cores = parallel::detectCores() - 2
    )
  )) %>%
  dplyr::mutate(
    share_pred_data_boot = list(purrr::map(boot_results, "share_pred_data") %>% rbindlist()),
    avg_yield_pred_data_boot = list(purrr::map(boot_results, "avg_yield_pred_data") %>% rbindlist())
  ) %>%
  dplyr::mutate(share_sum = list(
    share_pred_data_boot[, .(
      ir_share_hat_se = sd(ir_share_hat, na.rm = TRUE)
    ),
    by = .(sat)
    ] %>%
      .[share_pred_data, on = "sat"] %>%
      .[, `:=`(
        lower = ir_share_hat - 1.96 * ir_share_hat_se,
        upper = ir_share_hat + 1.96 * ir_share_hat_se
      )]
  )) %>%
  dplyr::mutate(avg_yield_sum = list(
    avg_yield_pred_data_boot[, .(
      avg_yield_se = sd(avg_yield, na.rm = TRUE),
      dif_avg_yield_se = sd(dif_avg_yield, na.rm = TRUE)
    ),
    by = .(balance, sat)
    ] %>%
      .[avg_yield_pred_data, on = c("balance", "sat")] %>%
      .[, `:=`(
        upper = avg_yield + 1.96 * avg_yield_se,
        lower = avg_yield - 1.96 * avg_yield_se,
        dif_upper = dif_avg_yield + 1.96 * dif_avg_yield_se,
        dif_lower = dif_avg_yield - 1.96 * dif_avg_yield_se
      )]
  )) %>%
  data.table() %>%
  dplyr::select(
    crop, data, sat_seq, sat_text_data,
    yield_pred_data,
    yield_dif_test,
    share_pred_data,
    share_sum,
    avg_yield_pred_data,
    avg_yield_pred_data_boot,
    avg_yield_sum
  )

>>>>

main_analysis <-
  reg_data %>%
  rowwise() %>%
  dplyr::mutate(sc_base = "31011") %>%
  #--- the same sequence used for all the bootstrap iterations ---#
  dplyr::mutate(balance_seq = list(
    seq(
      min(data$balance),
      max(data$balance),
      length = 100
    )
  )) %>%
  dplyr::mutate(sat_seq_eval = list(
    c(10, 40, 70, 100)
  )) %>%
  dplyr::mutate(share_reg_data = list(
    data %>%
      .[, comp := sum(ir == "nir" | ir == "ir"), by = .(sc_code, year)] %>%
      .[comp == 2, ] %>%
      .[, acres_ratio := acres / sum(acres), by = .(sc_code, year)] %>%
      .[ir == "ir" & ir_area_ratio >= 0.75, ] %>%
      .[, balance_avg := mean(balance), by = sc_code]
  )) %>%
  #--- the same sequence used for all the bootstrap iterations ---#
  dplyr::mutate(sat_seq = list(
    share_reg_data[, seq(min(sat),
      max(sat),
      length = 100
    )] %>%
      c(., sat_seq_eval)
  )) %>%
  #--- values of the controls to be used in prediction ---#
  dplyr::mutate(
    sandtotal_med = median(share_reg_data$sandtotal_r),
    silttotal_med = median(share_reg_data$silttotal_r),
    awc_med = median(share_reg_data$awc_r)
  ) %>%
  #++++++++++++++++++++++++++++++++++++
  #+ Main analysis
  #++++++++++++++++++++++++++++++++++++
  dplyr::mutate(yield_analysis_results = list(
    yield_analysis(data, balance_seq, sat_seq_eval, sat_breaks, sat_text_data, sc_base)
  )) %>%
  dplyr::mutate(
    yield_pred_data = list(yield_analysis_results$yield_pred_data),
    yield_semi_res = list(yield_analysis_results$semi_res)
  ) %>%
  dplyr::mutate(yield_dif_test = list(
    lapply(
      2:3,
      \(x) {
        test_dif_in_yield(
          balance_ls = seq(min(data$balance), max(data$balance), length = 50),
          base_q = 1,
          comp_q = x,
          yield_semi_res,
          sat_text_data,
          sc_base
        ) %>%
          .[, comp_q := x]
      }
    ) %>%
      rbindlist()
  )) %>%
  dplyr::mutate(share_pred_data = list(
    share_analysis_gam(
      share_reg_data,
      sat_seq,
      sandtotal_med,
      silttotal_med,
      awc_med
    )
  )) %>%
  dplyr::mutate(avg_yield_pred_data = list(
    get_average_yield(yield_pred_data, share_pred_data)
  ))

@@

all_results <-
  main_analysis %>%
  #--- bootsrap data ---#
  dplyr::mutate(boot_results = list(
    parallel::mclapply(
      1:1000,
      \(x) {
        print(x)

@@

        return(list(share_pred_data = share_pred_data, avg_yield_pred_data = avg_yield_pred_data))
      },
      mc.cores = parallel::detectCores() - 2
    )
  )) %>%
  dplyr::mutate(
    share_pred_data_boot = list(purrr::map(boot_results, "share_pred_data") %>% rbindlist()),
    avg_yield_pred_data_boot = list(purrr::map(boot_results, "avg_yield_pred_data") %>% rbindlist())
  ) %>%
  dplyr::mutate(share_sum = list(
    share_pred_data_boot[, .(
      ir_share_hat_se = sd(ir_share_hat, na.rm = TRUE),
      dif_ir_share_hat_se = sd(dif_ir_share_hat, na.rm = TRUE)
    ),
    by = .(sat)
    ] %>%
      .[share_pred_data, on = "sat"] %>%
      .[, `:=`(
        lower = ir_share_hat - 1.96 * ir_share_hat_se,
        upper = ir_share_hat + 1.96 * ir_share_hat_se,
        dif_lower = dif_ir_share_hat - 1.96 * dif_ir_share_hat_se,
        dif_upper = dif_ir_share_hat + 1.96 * dif_ir_share_hat_se
      )]
  )) %>%
  dplyr::mutate(avg_yield_sum = list(
    avg_yield_pred_data_boot[, .(
      avg_yield_se = sd(avg_yield, na.rm = TRUE),
      dif_avg_yield_se = sd(dif_avg_yield, na.rm = TRUE)
    ),
    by = .(balance, sat)
    ] %>%
      .[avg_yield_pred_data, on = c("balance", "sat")] %>%
      .[, `:=`(
        upper = avg_yield + 1.96 * avg_yield_se,
        lower = avg_yield - 1.96 * avg_yield_se,
        dif_upper = dif_avg_yield + 1.96 * dif_avg_yield_se,
        dif_lower = dif_avg_yield - 1.96 * dif_avg_yield_se
      )]
  )) %>%
  data.table() %>%
  dplyr::select(
    crop, data, sat_seq, sat_text_data,
    yield_pred_data,
    yield_dif_test,
    share_pred_data,
    share_sum,
    avg_yield_pred_data,
    avg_yield_pred_data_boot,
    avg_yield_sum
  )

### 2023-08-30 Codes/2_figures_tables.rmd
updates on the manuscript

coeff_soy <- 200
g_yield_wd_soy <-
  ggplot() +
  geom_line(
    data = yield_data[crop == "soy" & ir_or_not == "Irrigated", ],
    aes(y = yield, x = year, color = "Irrigated Yield")
  ) +
  geom_point(
    data = yield_data[crop == "soy" & ir_or_not == "Irrigated", ],
    aes(y = yield, x = year, color = "Irrigated Yield"),
    size = 0.8
  ) +
  geom_line(
    data = yield_data[crop == "soy" & ir_or_not == "Dryland", ],
    aes(y = yield, x = year, color = "Dryland Yield")
  ) +
  geom_point(
    data = yield_data[crop == "soy" & ir_or_not == "Dryland", ],
    aes(y = yield, x = year, color = "Dryland Yield"),
    size = 0.8
  ) +
  geom_line(
    data = wd_data[crop == "soy"],
    aes(y = wd / coeff_soy, x = year, color = "Water Deficit"),
    linetype = 2
  ) +
  geom_point(
    data = wd_data[crop == "soy"],
    aes(y = wd / coeff_soy, x = year, color = "Water Deficit"),
    size = 0.8
  ) +
  scale_y_continuous(
    sec.axis = sec_axis(~ . * coeff_soy, name = "Water Deficit (mm)")
  ) +
  scale_x_continuous(
    name = "Year",
    breaks = 1985:2016
  ) +
  scale_color_manual(
    name = "",
    values = c(
      "Dryland Yield" = "red",
      "Irrigated Yield" = "blue",
      "Water Deficit" = "black"
    )
  ) +
  ylab("Yield (bu/acre)") +
  xlab("Year") +
  theme_fig +
  theme(
    legend.position = "bottom",
    axis.text.x = element_text(angle = 90)
  ) +
  ggtitle("B. Soybean")

@@

## Saturated thickness

```{r, eval = FALSE}
g_sat_dist <-
  rbind(data_corn[year <= 2016, ], data_soy[year <= 2016, ]) %>%
  .[sat != 0, ] %>%
  ggplot(data = .) +
  geom_histogram(aes(x = sat), fill = "white", color = "blue") +
  facet_grid(type ~ ., scale = "free_y") +
  ylab("Count") +
  xlab("Aquifer Thickness (meter)") +
  theme_fig
```

## Map

@@

all_counties <-
  tigris::counties() %>%
  rename(
    state_code = STATEFP,
    county_code = COUNTYFP,
    county_name = NAME
  ) %>%
  left_join(., fips_codes, by = c("state_code", "county_code")) %>%
  dplyr::select(state_code, state, county_code, county_name) %>%
  mutate(sc_code = paste0(state_code, county_code)) %>%
  data.table()

@@

counties_corn_ir <-
  data_corn %>%
  .[sat_cat != "dryland", ] %>%
  .[, .(sat, sc_code)] %>%
  .[, .(sat = mean(sat, na.rm = TRUE)), by = sc_code] %>%
  left_join(all_counties, by = "sc_code") %>%
  .[, type := "Corn"] %>%
  st_as_sf()

@@

counties_soy_ir <-
  data_soy %>%
  .[sat_cat != "dryland", ] %>%
  .[, .(sat, sc_code)] %>%
  .[, .(sat = mean(sat, na.rm = TRUE)), by = sc_code] %>%
  left_join(all_counties, by = "sc_code") %>%
  .[, type := "Soybean"] %>%
  st_as_sf()

@@

ggsave(file = "GitControlled/Writing/Figures/g_map.png", g_map, height = 7, width = 6, dpi = 600)
ggsave(file = "GitControlled/Writing/Figures/g_map.pdf", g_map, height = 7, width = 6)
```

@@

g_wd_corn <-
  g_wds$g_fig[[1]] +
  ggtitle("A. Corn") +
  theme(
    plot.title = element_text(size = 9, family = "Times", face = "bold"),
    axis.text.x = element_blank(),
    axis.text.y = element_blank(),
    axis.ticks.x = element_blank(),
    axis.ticks.y = element_blank(),
    panel.grid.major = element_blank(),
    panel.border = element_blank(),
    plot.margin = margin(0, 0, 0, 0, "cm")
  )

g_wd_soy <-
  g_wds$g_fig[[2]] +
  ggtitle("B. Soybean") +
  theme(
    plot.title = element_text(size = 9, family = "Times", face = "bold"),
    axis.text.x = element_blank(),
    axis.text.y = element_blank(),
    axis.ticks.x = element_blank(),
    axis.ticks.y = element_blank(),
    panel.grid.major = element_blank(),
    panel.grid.minor = element_blank(),
    panel.border = element_blank(),
    plot.margin = margin(0, 0, 0, 0, "cm")
    )

g_yield_response <-
  cowplot::plot_grid(
    g_wd_corn, g_ir_yield_corn, g_wd_soy, g_ir_yield_soy,
    ncol = 1,
    align = "v",
    rel_heights = c(0.15 / 2, 0.72 / 2, 0.15 / 2, 0.98 / 2)
  )

@@

@@

g_share <-
  ggplot(plot_data_ir_share[sat <= 150, ]) +
  geom_line(aes(y = ir_share_hat, x = sat)) +
  geom_ribbon(
    aes(
      ymin = lower,
      ymax = upper,
      x = sat
    ),
    alpha = 0.4
  ) +
  scale_y_continuous(breaks = seq(0, 1, by = 0.1)) +
  scale_x_continuous(breaks = seq(10, 160, by = 10)) +
  xlab("Aquifer Thickness (meter)") +
  ylab("Decline in Estimated Share of Irrigated Acres") +
  facet_wrap(crop_type ~ ., ncol = 1) +
  theme_fig +
  theme(
    legend.position = "bottom",
    strip.background = element_blank(),
    strip.text = element_text(hjust = 0, face = "bold", family = "Times", size = )
  )

ggsave(
  file = "GitControlled/Writing/Figures/g_share.pdf",
  g_share,
  height = 4,
  width = 5
)
```

# Difference in the share of irrigated production (from 130)

```{r}
g_share_dif <-
  ggplot(plot_data_ir_share[sat < 105, ]) +
  geom_line(aes(y = dif_ir_share_hat, x = sat)) +
  geom_ribbon(
    aes(
      ymin = dif_lower,
      ymax = dif_upper,
      x = sat
    ),
    alpha = 0.4
  ) +
  geom_hline(yintercept = 0, color = "red") +
  scale_y_continuous(breaks = seq(0, 1, by = 0.1)) +
  scale_x_continuous(breaks = seq(10, 160, by = 10)) +
  xlab("Aquifer Thickness (meter)") +
  ylab("Estimated Share of Irrigated Acres") +
  facet_wrap(crop_type ~ ., ncol = 1) +
  theme_fig +
  theme(
    legend.position = "bottom",
    strip.background = element_blank(),
    strip.text = element_text(hjust = 0, face = "bold", family = "Times", size = )
  )

@@

```{r}
g_total_both <-
  all_results[, .(crop, avg_yield_sum)] %>%
  unnest() %>%
  data.table() %>%
  .[, crop_type := case_when(
    crop == "corn" ~ "A. Corn",
    crop == "soy" ~ "B. Soybean"
  )] %>%
  nest_by(crop_type) %>%
  data.table() %>%
  dplyr::mutate(g_fig = purrr::map(data, \(data) {
    ggplot(data) +
      geom_line(aes(y = avg_yield, x = balance, color = factor(sat))) +
      theme_fig +
      ylim(min(data$avg_yield) - 0.5, max(data$avg_yield) + 0.5) +
      ylab("Yield (tonne/ha)") +
      scale_color_discrete(
        "Aquifer Thickness (meter)",
        guide = guide_legend(
          title.position = "top",
          nrow = 1
        )
      ) +
      scale_x_continuous(name = "Water Deficit (mm)", breaks = (-2:11) * 100, limits = c(-200, 1200)) +
      theme(legend.position = "bottom")
  }))

g_total_corn <-
  g_total_both$g_fig[[1]] +
  theme(
    legend.position = "none",
    axis.title.x = element_blank()
  ) +
  ylim(6, 13) +
  ggtitle("A. Corn")

g_total_soy <-
  g_total_both$g_fig[[2]] +
  ylim(1.5, 4) +
  ggtitle("B. Soybean")

g_total <- g_total_corn / g_total_soy

ggsave(
  file = "GitControlled/Writing/Figures/g_total_impact.pdf",
  g_total,
  height = 6,
  width = 6
)
```

>>>>

coeff_soy <- 200

g_yield_wd_soy <-
  ggplot() +
  geom_line(
    data = yield_data[crop == "soy" & ir_or_not == "Irrigated", ],
    aes(y = yield, x = year, color = "Irrigated Yield")
  ) +
  geom_point(
    data = yield_data[crop == "soy" & ir_or_not == "Irrigated", ],
    aes(y = yield, x = year, color = "Irrigated Yield"),
    size = 0.8
  ) +
  geom_line(
    data = yield_data[crop == "soy" & ir_or_not == "Dryland", ],
    aes(y = yield, x = year, color = "Dryland Yield")
  ) +
  geom_point(
    data = yield_data[crop == "soy" & ir_or_not == "Dryland", ],
    aes(y = yield, x = year, color = "Dryland Yield"),
    size = 0.8
  ) +
  geom_line(
    data = wd_data[crop == "soy"],
    aes(y = wd / coeff_soy, x = year, color = "Water Deficit"),
    linetype = 2
  ) +
  geom_point(
    data = wd_data[crop == "soy"],
    aes(y = wd / coeff_soy, x = year, color = "Water Deficit"),
    size = 0.8
  ) +
  scale_y_continuous(
    sec.axis = sec_axis(~ . * coeff_soy, name = "Water Deficit (mm)")
  ) +
  scale_x_continuous(
    name = "Year",
    breaks = 1985:2016
  ) +
  scale_color_manual(
    name = "",
    values = c(
      "Dryland Yield" = "red",
      "Irrigated Yield" = "blue",
      "Water Deficit" = "black"
    )
  ) +
  ylab("Yield (bu/acre)") +
  xlab("Year") +
  theme_fig +
  theme(
    legend.position = "bottom",
    axis.text.x = element_text(angle = 90)
  ) +
  ggtitle("B. Soybean")

@@

## Saturated Thickness Map

@@

all_counties <-
  tigris::counties() %>%
  st_simplify(dTolerance = 100) %>%
  rename(
    state_code = STATEFP,
    county_code = COUNTYFP,
    county_name = NAME
  ) %>%
  left_join(., fips_codes, by = c("state_code", "county_code")) %>%
  dplyr::select(state_code, state, county_code, county_name) %>%
  mutate(sc_code = paste0(state_code, county_code)) %>%
  data.table()

@@

counties_corn_ir <-
  copy(data_corn) %>%
  .[sat_cat != "dryland", ] %>%
  .[, .(sat, sc_code)] %>%
  .[, .(sat = mean(sat, na.rm = TRUE)), by = sc_code] %>%
  left_join(all_counties, by = "sc_code") %>%
  data.table() %>%
  .[, type := "Corn"] %>%
  st_as_sf()

@@

counties_soy_ir <-
  copy(data_soy) %>%
  .[sat_cat != "dryland", ] %>%
  .[, .(sat, sc_code)] %>%
  .[, .(sat = mean(sat, na.rm = TRUE)), by = sc_code] %>%
  left_join(all_counties, by = "sc_code") %>%
  data.table() %>%
  .[, type := "Soybean"] %>%
  st_as_sf()

@@

ggsave(file = "GitControlled/Writing/Figures/g_map.pdf", g_map, height = 7, width = 6)
```

@@

g_wd_corn <-
  g_wds$g_fig[[1]] +
  ggtitle("A. Corn") +
  theme(
    plot.title = element_text(size = 9, family = "Times", face = "bold"),
    axis.text.x = element_blank(),
    axis.text.y = element_blank(),
    axis.ticks.x = element_blank(),
    axis.ticks.y = element_blank(),
    panel.grid.major = element_blank(),
    panel.grid.minor = element_blank(),
    panel.border = element_blank(),
    plot.margin = margin(0, 0, -0.5, 0, "cm")
  )

g_wd_soy <-
  g_wds$g_fig[[2]] +
  ggtitle("B. Soybean") +
  theme(
    plot.title = element_text(size = 9, family = "Times", face = "bold"),
    axis.text.x = element_blank(),
    axis.text.y = element_blank(),
    axis.ticks.x = element_blank(),
    axis.ticks.y = element_blank(),
    panel.grid.major = element_blank(),
    panel.grid.minor = element_blank(),
    panel.border = element_blank(),
    plot.margin = margin(0, 0, -0.5, 0, "cm")
  )

g_yield_response <-
  cowplot::plot_grid(
    g_wd_corn, g_ir_yield_corn, g_wd_soy, g_ir_yield_soy,
    ncol = 1,
    align = "v",
    rel_heights = c(0.18 / 2, 0.69 / 2, 0.18 / 2, 0.95 / 2)
  )

@@

```{r}
#++++++++++++++++++++++++++++++++++++
#+ Share response
#++++++++++++++++++++++++++++++++++++
plot_data_ir_share <-
  all_results[, .(crop, share_pred_data)] %>%
  unnest(cols = share_pred_data) %>%
  data.table() %>%
  .[, crop_type := case_when(
    crop == "corn" ~ "A. Corn",
    crop == "soy" ~ "B. Soybean"
  )]

g_share <-
  plot_data_ir_share %>%
  nest_by(crop) %>%
  dplyr::mutate(g_fig = list(
    ggplot(dplyr::filter(data, sat <= 150)) +
      geom_line(aes(y = ir_share_hat, x = sat)) +
      geom_ribbon(
        aes(
          ymin = ir_share_hat - 1.96 * ir_share_hat_se,
          ymax = ir_share_hat + 1.96 * ir_share_hat_se,
          x = sat
        ),
        alpha = 0.4
      ) +
      scale_y_continuous(breaks = seq(0, 1, by = 0.1), limits = c(0.4, 1)) +
      scale_x_continuous(breaks = seq(10, 150, by = 10)) +
      coord_cartesian(xlim = c(9, 150)) +
      xlab("Aquifer Thickness (meter)") +
      ylab("Share of Irrigated Acres") +
      theme_fig +
      theme(
        legend.position = "bottom"
      )
  ))

#++++++++++++++++++++++++++++++++++++
#+ Saturated thickness histogram
#++++++++++++++++++++++++++++++++++++
g_sat_hist <-
  all_results[, .(crop, data)] %>%
  dplyr::mutate(g_fig = purrr::map(
    data,
    function(data) {
      ggplot(data[sat < 150 & ir == "ir", ]) +
        geom_histogram(aes(x = sat), bins = 30, col = "darkgreen", fill = NA) +
        theme_fig +
        xlab("") +
        ylab("") +
        coord_cartesian(xlim = c(9, 150)) +
        theme(
          plot.title = element_text(size = 9, family = "Times", face = "bold"),
          axis.text.x = element_blank(),
          axis.text.y = element_blank(),
          axis.ticks.x = element_blank(),
          axis.ticks.y = element_blank(),
          panel.grid.major = element_blank(),
          panel.grid.minor = element_blank(),
          panel.border = element_blank(),
          plot.margin = margin(0, 0, -0.5, 0, "cm")
        )
    }
  ))

g_ir_share <-
  cowplot::plot_grid(
    g_sat_hist$g_fig[[1]] + ggtitle("A. Corn"),
    g_share$g_fig[[1]] + theme(plot.margin = margin(0, 0, 0.5, 0, "cm")),
    g_sat_hist$g_fig[[2]] + ggtitle("B. Soybean"),
    g_share$g_fig[[2]],
    ncol = 1,
    align = "v",
    rel_heights = c(0.18 / 2, 0.64 / 2, 0.18 / 2, 0.64 / 2)
  )

ggsave(
  file = "GitControlled/Writing/Figures/g_share.pdf",
  g_ir_share,
  height = 6,
  width = 6
)
```

# Difference in the share of irrigated production (from 100)

@@

g_share_dif <-
  ggplot(plot_data_ir_share[sat < 100, ]) +
  geom_line(aes(y = dif_ir_share_hat, x = sat)) +
  geom_ribbon(
    aes(
      ymin = dif_lower,
      ymax = dif_upper,
      x = sat
    ),
    alpha = 0.4
  ) +
  geom_hline(yintercept = 0, color = "red") +
  scale_y_continuous(breaks = seq(0, 1, by = 0.1)) +
  scale_x_continuous(breaks = seq(10, 160, by = 10)) +
  xlab("Aquifer Thickness (meter)") +
  ylab("Decline in Estimated Share of Irrigated Acres") +
  facet_wrap(crop_type ~ ., ncol = 1) +
  theme_fig +
  theme(
    legend.position = "bottom",
    strip.background = element_blank(),
    strip.text = element_text(hjust = 0, face = "bold", family = "Times", size = )
  )

@@

```{r}
g_total_both <-
  all_results[, .(crop, avg_yield_sum)] %>%
  unnest() %>%
  data.table() %>%
  .[, crop_type := case_when(
    crop == "corn" ~ "A. Corn",
    crop == "soy" ~ "B. Soybean"
  )] %>%
  nest_by(crop_type) %>%
  data.table() %>%
  dplyr::mutate(g_fig = purrr::map(data, \(data) {
    ggplot(data) +
      geom_line(aes(y = avg_yield, x = balance, color = factor(sat))) +
      theme_fig +
      ylim(min(data$avg_yield) - 0.5, max(data$avg_yield) + 0.5) +
      ylab("Yield (tonne/ha)") +
      scale_color_discrete(
        "Aquifer Thickness (meter)",
        guide = guide_legend(
          title.position = "top",
          nrow = 1
        )
      ) +
      scale_x_continuous(
        name = "Water Deficit (mm)",
        breaks = (-2:12) * 100
      ) +
      coord_cartesian(xlim = c(-200, 1150)) +
      theme(legend.position = "bottom")
  }))

g_total_corn <-
  g_total_both$g_fig[[1]] +
  theme(legend.position = "none") +
  ylim(6, 13)

g_total_soy <-
  g_total_both$g_fig[[2]] +
  ylim(1.5, 4)

g_wds <-
  all_results[, .(crop, data)] %>%
  dplyr::mutate(g_fig = purrr::map(
    data,
    function(data) {
      ggplot(data) +
        geom_histogram(aes(x = balance), bins = 50, col = "darkgreen", fill = NA) +
        theme_fig +
        xlab("") +
        ylab("") +
        coord_cartesian(xlim = c(-200, 1150)) +
        theme(
          plot.title = element_text(size = 9, family = "Times", face = "bold"),
          axis.text.x = element_blank(),
          axis.text.y = element_blank(),
          axis.ticks.x = element_blank(),
          axis.ticks.y = element_blank(),
          panel.grid.major = element_blank(),
          panel.grid.minor = element_blank(),
          panel.border = element_blank(),
          plot.margin = margin(0, 0, -0.5, 0, "cm")
        )
    }
  ))

g_total_impact <-
  cowplot::plot_grid(
    g_wds$g_fig[[1]] + ggtitle("A. Corn"),
    g_total_corn + theme(plot.margin = margin(0, 0, 0.5, 0, "cm")),
    g_wds$g_fig[[2]] + ggtitle("B. Soybean"),
    g_total_soy,
    ncol = 1,
    align = "v",
    rel_heights = c(0.18 / 2, 0.65 / 2, 0.18 / 2, 0.8 / 2)
  )

ggsave(
  file = "GitControlled/Writing/Figures/g_total_impact.pdf",
  g_total_impact,
  height = 6,
  width = 6
)
```
